### 2023-08-15 manuscript.tex
Instead of writing of 'haplochromine' cichlids [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/37cc38a386f502ad80dd15509062ce55dc9330d8.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/37cc38a386f502ad80dd15509062ce55dc9330d8/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5869141381

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...cf71b71e6291167fe12fef6359937f11e6552b5b\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/cf71b71e6291167fe12fef6359937f11e6552b5b/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/cf71b71e6291167fe12fef6359937f11e6552b5b}{habi/EAWAG-manuscript@cf71b71}
on August 15, 2023.

@@

The collection of cichlid fish available is extremely valuable, hence a nondestructive imaging method is paramount for studying these samples.
Since micro--computed tomography can be regarded as a nondestructive investigation method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]} (N=133).

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...37cc38a386f502ad80dd15509062ce55dc9330d8\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/37cc38a386f502ad80dd15509062ce55dc9330d8/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/37cc38a386f502ad80dd15509062ce55dc9330d8}{habi/EAWAG-manuscript@37cc38a}
on August 15, 2023.

@@

The collection of Lake Victoria cichlids investigated here is extremely valuable, hence a nondestructive imaging method for studying these samples is paramount.
Since micro--computed tomography can be regarded as a nondestructive investigation method for biological samples, it is the ideal imaging method for investigating the oral and pharyngeal jaws as well as the skull features of the fish presented in this study {[}\protect\hyperlink{ref-19h9vxsYG}{6}{]} (N=133).
